WordRec Experiment

### 2019-04-11 Data_and_analysis/analyses.Rmd
more revisions

#Simulate sounds
exp4_both_s <- exp4_s %>%
  mutate(prob = model_s(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer_simu = rbinom(1, 1, prob=prob))

exp4_both_c <- exp4_c %>%
  mutate(prob = model_c(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer_simu = rbinom(1, 1, prob=prob))

exp4_both_j <- exp4_j %>%
  mutate(prob = model_des(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer_simu = rbinom(1, 1, prob=prob))

@@

@@

#Split data by subject 
data_by_subj_s <- split(exp4_both_s, exp4_both_s$ID) 
data_by_subj_c <- split(exp4_both_c, exp4_both_c$ID)
data_by_subj_j <- split(exp4_both_j, exp4_both_j$ID)

@@

@@

ID <- as.list(strsplit(names(model_by_subj_s), " "))

#Here extract ceofficients to build optimal model later
coef_s <- map2(model_by_subj_s, ID, co_uni) %>%
  bind_rows() %>%
  rename(vrA_u= variance,
         bA_u =  bias,
         conv_A = convergence)

coef_simu_s <- map2(model_by_subj_simu_s, ID, co_uni) %>%
  bind_rows() %>%
  rename(vrA_u= variance,
         bA_u =  bias,
         conv_A = convergence)

coef_c <- map2(model_by_subj_c, ID, co_uni) %>%
  bind_rows() %>%
  rename(vrV_u= variance,
         bV_u =  bias,
         conv_V = convergence)

coef_simu_c <- map2(model_by_subj_simu_c, ID, co_uni) %>%
  bind_rows() %>%
  rename(vrV_u= variance,
         bV_u =  bias,
         conv_V = convergence)

coef_j <- map2(model_by_subj_j, ID, co_bim) %>%
  bind_rows() %>%
  rename(vrA_j = var_s,
         vrV_j = var_c,  
         b =  bias,
         conv_j = convergence)

coef_simu_j <- map2(model_by_subj_simu_j, ID, co_bim) %>%
  bind_rows() %>%
  rename(vrA_j = var_s,
         vrV_j = var_c,  
         b =  bias,
         conv_j = convergence)

@@

data_models_simu <- exp_good %>%
  filter(condition == "joint",
         experiment == "Experiment4") %>%
  group_by(ID, concept_dist, sound_dist) %>%
  summarise(mean = mean(answer)) %>%
  ungroup() %>%
  left_join(coef_simu_s) %>%
  left_join(coef_simu_c) %>%
  left_join(coef_simu_j)

@@

N_conv_simu <- data_models_good_simu %>% 
  distinct(ID) %>%
  nrow()

models <- function (subject_data) {
  subject_data %>% rename(Joint = mean) %>%
  mutate(Descriptive = model_des(subject_data, sound_dist, concept_dist)) %>%
  mutate(Optimal = model_opt(subject_data, sound_dist, concept_dist)) %>%
  mutate(Auditory = model_s(subject_data, sound_dist, concept_dist)) %>%
  mutate(Visual = model_c(subject_data, sound_dist, concept_dist)) %>%
  gather(model, pred, Visual, Auditory, Optimal, Descriptive) 
}

@@

#feather::write_feather(weight, "ind_weights.feather")
#weight <- feather::read_feather("ind_weights.feather")

weight_simu_low <- quantile(weight_simu$prop, 0.05)
weight_simu_high <- quantile(weight_simu$prop, 0.95)

ggplot(data=weight_both, aes(x=prop, y=..ncount..)) +
  #geom_histogram(data=subset(weight_both, data=='real'), fill="red", alpha=0.2, binwidth = 0.4)+
  geom_histogram(data=subset(weight_both, data=='simulated'), fill="blue", alpha=0.1, binwidth = 0.4)+
  #geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
  #geom_histogram(binwidth = 0.2) +
  geom_vline(xintercept = weight_simu_low, linetype='dashed') +
  geom_vline(xintercept = weight_simu_high, linetype='dashed')+
 scale_x_log10(breaks =c(0.1,1,10)) +
   xlab("Optimal weighing relative to real weighing") +ylab("Count")+
  theme_few()+
  theme(aspect.ratio = 0.7) #+
  #coord_cartesian(xlim=c(0.01,100))

@@

Simulat random responses from the population level model

First, take the real experimental data
```{r}
exp_exp4_s <- exp_good %>%
  filter(condition =="sound",
         experiment == "Experiment4")

exp_exp4_c <- exp_good %>%
  filter(condition =="concept",
         experiment == "Experiment4")

exp_exp4_j <- exp_good %>%
  filter(condition =="joint",
         experiment == "Experiment4")
```

Then, instead of the real answers, simulate new answers from the population-level model

@@

simulations <- data.frame()
#x <- c("ID", "bimod")
#colnames(simlations) <- x

for (i in 1:50) {
Simul_exp1 <- joint_all_exp1 %>%
  select(ID, sound_dist, concept_dist) %>%
  mutate(prob = model_fit1(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer = rbinom(1, 1, prob=prob))

joint_bysub_sim_1 <- Simul_exp1 %>%
  group_by(ID) %>%
  do(fit_joint_sim_1 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))

bimodal_bysub_sim_1 = tidy(joint_bysub_sim_1, fit_joint_sim_1) %>%
  filter(term == 'concept_dist' | term == 'sound_dist') %>%
  mutate(j_var = 4/(estimate)) %>%
  select(ID, term, j_var) %>%
  spread(term, j_var) %>%
  rename(j_c_var = concept_dist, 
         j_s_var = sound_dist) %>%
  mutate(bimod = j_c_var/j_s_var) %>%
  select(ID, bimod) %>%
  filter(bimod > 0.1) %>%
  filter(bimod < 10)

  simulations <- bind_rows(simulations, bimodal_bysub_sim_1)
}

  #I need to take the average of this over multiple runs

  bimod_sim <- simulations  %>%
    mutate(data='simulation')

  bimod_real <- bimodal_bysub_good_1  %>%
    select(ID, bimod) %>%
    mutate(data='real')

  #n_remove <- nrow(bimod_sim)-nrow(bimod_real)

  #bimod_sim <- head(bimod_sim, -n_remove)

  bimod_all <- bind_rows(bimod_real, bimod_sim)

>>>>

@@

simu_s <- data.frame()
simu_c <- data.frame()
simu_j <- data.frame()
#x <- c("ID", "bimod")
#colnames(simlations) <- x

for (i in 1:50) {

simu_temp_s <- exp4_s %>%
  mutate(ID_2 = paste(ID,'_',i, sep="")) %>%
  mutate(prob = model_s(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer_simu = rbinom(1, 1, prob=prob)) %>%
  select(-ID) %>%
  rename(ID=ID_2)

simu_temp_c <- exp4_c %>%
  mutate(ID_2 = paste(ID,'_',i, sep="")) %>%
  mutate(prob = model_c(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer_simu = rbinom(1, 1, prob=prob)) %>%
  select(-ID) %>%
  rename(ID=ID_2)

simu_temp_j <- exp4_j %>%
  mutate(ID_2 = paste(ID,'_',i, sep="")) %>%
  mutate(prob = model_des(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer_simu = rbinom(1, 1, prob=prob)) %>%
  select(-ID) %>%
  rename(ID=ID_2)

simu_s <- bind_rows(simu_s, simu_temp_s)
simu_c <- bind_rows(simu_c, simu_temp_c)
simu_j <- bind_rows(simu_j, simu_temp_j)

@@

#Split data by subject real
data_by_subj_s <- split(exp4_s, exp4_s$ID) 
data_by_subj_c <- split(exp4_c, exp4_c$ID)
data_by_subj_j <- split(exp4_j, exp4_j$ID)

@@

#Split data by subject simulated
data_by_subj_s <- split(simu_s, simu_s$ID) 
data_by_subj_c <- split(simu_c, simu_c$ID)
data_by_subj_j <- split(simu_j, simu_j$ID)

@@

ID_real <- as.list(strsplit(names(model_by_subj_s), " "))
ID_simu <- as.list(strsplit(names(model_by_subj_simu_s), " "))

#Here extract ceofficients to build optimal model later
coef_s <- map2(model_by_subj_s, ID_real, co_uni) %>%
  bind_rows() %>%
  rename(vrA_u= variance,
         bA_u =  bias,
         conv_A = convergence)

coef_simu_s <- map2(model_by_subj_simu_s, ID_simu, co_uni) %>%
  bind_rows() %>%
  rename(vrA_u= variance,
         bA_u =  bias,
         conv_A = convergence)

coef_c <- map2(model_by_subj_c, ID_real, co_uni) %>%
  bind_rows() %>%
  rename(vrV_u= variance,
         bV_u =  bias,
         conv_V = convergence)

coef_simu_c <- map2(model_by_subj_simu_c, ID_simu, co_uni) %>%
  bind_rows() %>%
  rename(vrV_u= variance,
         bV_u =  bias,
         conv_V = convergence)

coef_j <- map2(model_by_subj_j, ID_real, co_bim) %>%
  bind_rows() %>%
  rename(vrA_j = var_s,
         vrV_j = var_c,  
         b =  bias,
         conv_j = convergence)

coef_simu_j <- map2(model_by_subj_simu_j, ID_simu, co_bim) %>%
  bind_rows() %>%
  rename(vrA_j = var_s,
         vrV_j = var_c,  
         b =  bias,
         conv_j = convergence)

@@

data_models_simu <- simu_j %>%
  group_by(ID, concept_dist, sound_dist) %>%
  summarise(mean = mean(answer)) %>%
  ungroup() %>%
  left_join(coef_simu_s) %>%
  left_join(coef_simu_c) %>%
  left_join(coef_simu_j)

@@

N_conv_simu <- data_models_good_simu %>% 
  distinct(ID) %>%
  nrow()
```

```{r}
models <- function (subject_data) {
  subject_data %>% rename(Joint = mean) %>%
  mutate(Descriptive = model_des(subject_data, sound_dist, concept_dist)) %>%
  mutate(Optimal = model_opt(subject_data, sound_dist, concept_dist)) %>%
  mutate(Auditory = model_s(subject_data, sound_dist, concept_dist)) %>%
  mutate(Visual = model_c(subject_data, sound_dist, concept_dist)) %>%
  gather(model, pred, Visual, Auditory, Optimal, Descriptive) 
}

@@

feather::write_feather(weight_both, "ind_weights.feather")
#weight <- feather::read_feather("ind_weights.feather")

weight_simu_low <- quantile(weight_simu$prop, 0.05)
weight_simu_up <- quantile(weight_simu$prop, 0.95)

#Number of subject relying on the visual modality (p < 0.05) and the auditory modality (p > 0.95)

subj_all <- weight %>%
  nrow()

subj_vis <- weight %>%
  filter(prop < weight_simu_low) %>%
  nrow()

subj_aud <- weight %>%
  filter(prop > weight_simu_up) %>%
  nrow()

ggplot(data=weight_both, aes(x=prop, y=..ncount..)) +
  geom_histogram(data=subset(weight_both, type=='real'), fill="red", alpha=0.2, binwidth = 0.4)+
  geom_histogram(data=subset(weight_both, type=='simulated'), fill="blue", alpha=0.1, binwidth = 0.4)+
  #geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
  #geom_histogram(binwidth = 0.2) +
  geom_vline(xintercept = weight_simu_low, linetype='dashed') +
  geom_vline(xintercept = weight_simu_high, linetype='dashed')+
 scale_x_log10(breaks =c(0.1,1,10)) +
   xlab("Optimal weighing relative to real weighing") +ylab("Count")+
  theme_few()+
  theme(aspect.ratio = 0.7) #+
  #coord_cartesian(xlim=c(0.01,100))

@@

@@
